Group B Analysis - Calibration

### 2024-10-12 group-b/E2-analysis-calibration.Rmd

# correlation between initial and halfway calibration
ggplot(summary.data.calib.wide %>% filter(is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between 2 successive calibration attempts
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between second attempt calibration and halfway
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `2`, y = `3`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none") 
```

@@

calib.by.subj = summary.data.calib %>% 
  group_by(subject_id) %>% 
  summarize(mean_percent_in_roi = mean(mean_percent_in_roi))

@@

Participants' calibration quality, measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect))

>>>>

# correlation between initial and halfway calibration (for folks that didn't need to redo calibration)
ggplot(summary.data.calib.wide %>% filter(is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between 2 successive calibration attempts (only folks who redid calibration)
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `1`, y = `2`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none")

# correlation between second attempt calibration and halfway (only folks who redid calibration)
ggplot(summary.data.calib.wide %>% filter(!is.na(`3`)), aes(x = `2`, y = `3`))+
  geom_point()+
  geom_smooth(method = 'lm')+
  theme_bw()+
  theme(legend.position = "none") 
```

@@

calib.by.subj = summary.data.calib %>% 
  group_by(subject_id) %>% 
  filter(calib_num == max(calib_num) | calib_num == max(calib_num)-1) %>% #AJ: excludes initial calibrations of those who recalibrated, to be in line with other Expts
  summarize(mean_percent_in_roi = mean(mean_percent_in_roi),
            calib_total = max(calib_num))

@@

Participants' calibration quality was measured as the mean percentage of fixations that landed within 200 pixels of the calibration point, averaging initial calibration (or re-calibration for participants who repeated calibration) and calibration at the halfway point. Calibration scores varied substantially (between `r range(calib.by.subj$mean_percent_in_roi) %>% round(digits = 2)` %). 
The quality of a participant's calibration was not significantly correlated with the participant's effect size ( _Pearson's r_= `r m_calib_r`, _p_ = `r m_calib_p`) as measured by the difference between the proportion of looks to the critical quadrant minus the average proportion of looks to the average of the other three quadrants (see Figure\ \@ref(fig:E2-calib-effect)).

```{r aggro exclusion}
#Identify Ps with calibration scores under 50%
validation.threshold.aggro <- 50

e2.bad.subjects.validation.aggro <- calib.by.subj %>%
  filter(mean_percent_in_roi <= validation.threshold.aggro) %>%
  pull(subject_id) %>%
  as.character()

e2.n.bad.subjects.aggro <- length(e2.bad.subjects.validation.aggro) #It's 12

#Get the critical data used in the main analyses, filter out "bad" subjs

#Gaze
free.view.summary.subject.data.aggro <- free.view.summary.subject.data %>%
  filter(!subject_id %in% e2.bad.subjects.validation.aggro)

#Accuracy
acc.behavioral.subject.data.aggro <- acc.behavioral.subject.data %>%
  filter(!subject_id %in% e2.bad.subjects.validation.aggro)
#RT
rt.behavioral.subject.data.aggro <- rt.behavioral.subject.data %>%
  filter(!subject_id %in% e2.bad.subjects.validation.aggro)
```

```{r aggro reanalysis}
#Re-run critical models

#Gaze
E2_gaze_model.aggro<-lmer(proportion ~ normalized_quadrant + (1+normalized_quadrant|subject_id), data = free.view.summary.subject.data.aggro)

E2_gaze_model.aggro_tab = broom.mixed::tidy(E2_gaze_model.aggro) 
E2_gaze_model.aggro_q1 = E2_gaze_model.aggro_tab %>% filter(term == "normalized_quadrantfirst")
E2_gaze_model.aggro_q2 = E2_gaze_model.aggro_tab %>% filter(term == "normalized_quadrantsecond")
E2_gaze_model.aggro_q3 = E2_gaze_model.aggro_tab %>% filter(term == "normalized_quadrantthird")

#Accuracy
E2_acc_model.aggro<-lmer(accuracy ~ relation*condition + (1|subject_id), data = acc.behavioral.subject.data.aggro)

E2_acc_model.aggro_tab = broom.mixed::tidy(E2_acc_model.aggro) 
E2_acc_model.aggro_rel = E2_acc_model.aggro_tab %>% filter(term == "relation1")
E2_acc_model.aggro_cond = E2_acc_model.aggro_tab %>% filter(term == "condition1")

#RT
E2_RT_model.aggro<-lmer(rt ~ relation*condition + (1|subject_id), data = rt.behavioral.subject.data.aggro)

E2_RT_model.aggro_tab = broom.mixed::tidy(E2_RT_model.aggro) 
E2_RT_model.aggro_rel = E2_RT_model.aggro_tab %>% filter(term == "relation1")
E2_RT_model.aggro_cond = E2_RT_model.aggro_tab %>% filter(term == "condition1")

```
#### Re-analysis After Exclusions
There were `r e2.n.bad.subjects.aggro` participants whose calibration score was under 50%. When those participants were removed from the analyses, critical results were in line with the main analyses: there remains a clear gaze bias in the free-viewing condition (first: _b_ =  `r E2_gaze_model.aggro_q1 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q1 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, second: _b_ =  `r E2_gaze_model.aggro_q2 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q2 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001, third: _b_ =  `r E2_gaze_model.aggro_q3 %>% pull(estimate) %>% round(digits = 2)`, _SE_ =  `r E2_gaze_model.aggro_q3 %>% pull(std.error) %>% round(digits = 2)`, _p_<0.001 ); viewing condition still did not interact with question type to predict either behavioral outcome.
